Goals and Tasks

### 2020-09-07 README.Rmd
- Changes on final report. - First update of Roxygen comments.

<!-- README.md is generated from README.Rmd. Please edit that file -->

@@

* Supervisor: Thomas Kneib
* Students: Johannes, Levin, Sebastián
* Topic: Parameter estimation and variable selection using the boosting ensemble learning algorithm

## Tasks

### until ~ mid June

* extend documentation of R6-Class
  + inherit documentation from Hannes
  + add own extensions
  + both can be done via roxygen (see Wickham R-PAckages chp5)

* maybe move component-selection mechanism from active field in R6-Class to gradient_boost-function
  + intuition tells me R6-Class is not the right place to do central calculations of the algorithm
  + maybe create new helper function component_selection() which gradien_boost() can call

### until ~ 11 May

* simple boost function for scale (estimate var(yi))
* read Wickham "R-Packages"
* try implementing function-testing
* get used to roxygen2

## Literature
* Section **4.3** on "Boosting Linear Regression Models" in "Regression: Models, methods, and applications" by Ludwig Fahrmeir, Thomas Kneib, Stefan Lang, and Brian Marx
* Section **2.9.1** on "Regression models for location, scale, and shape" in ibd.

@@

## Location Scale Regression Model

@@

## Working with Location Scale Regression Boost Model
First, you need to install the `asp20model` &  `asp20boost` package from GitLab and load it:

```{r installation, eval = 3}
#install.packages("devtools")
#This throws an error for asp20boost
#devtools::install_gitlab("asp20/asp20model", host = "gitlab.gwdg.de")
#devtools::install_gitlab("asp20/asp20boost", host = "gitlab.gwdg.de")

model$gamma
```

>>>>

@@

Welcome to *asp20boost*.
We implement both simple boosting and component-wise boosting ensemble algorithms for location and scale settings.

 * Supervisor: Thomas Kneib
 * Students: Johannes, Levin, Sebastián

We have successfully implemented both boosting variants.
Currently, we work on the publication of the package i.e. we perform unit tests and expand the documentation.

### Literature
* Section **4.3** on "Boosting Linear Regression Models" in "Regression: Models, methods, and applications" by Ludwig Fahrmeir, Thomas Kneib, Stefan Lang, and Brian Marx
* Section **2.9.1** on "Regression models for location, scale, and shape" in ibd.

@@

This is a visual representation of a location scale Regression Model (taken from asp20model)

@@

To install and work with out package you need first to install the `asp20model` &  `asp20boost` package from GitLab and load it. 
The installing of devtools requires attention.

```{r installation, eval = 3}
#install.packages("devtools")
#devtools::install_gitlab("asp20/asp20model", host = "gitlab.gwdg.de")
#devtools::install_gitlab("asp20/asp20boost", host = "gitlab.gwdg.de")
```
